---
title: "Investigation 3"
author: "John Viviani"
date: "6/15/2020"
output: 
  md_document:
    variant: gfm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

{
  c("conflicted",    # To deal with conflicting function names.
                     # I've had some strangeness with this
                     #  script. I suspect package:conflicted,
                     #  but I don't yet know for sure.
    "data.table",    # Fast data input/output
    "dplyr",         # This is all of tidyverse that gets used here
    "drat",          # Needed for a possible install below 
    "dtplyr",        # dplyr syntax with a data.table backend
    "igraph",        # Basic network tools; we'll use statnet mostly
    "igraphdata",    # Some useful datasets
    "intergraph",    # Translate between igraph and statnet formats
    "statnet",        # A suite of network tools, including ERGM and more
    "tidyverse"
  ) -> package_names
  
  for (package_name in package_names) {
    if (!is.element(package_name, installed.packages()[, 1])) {
      install.packages(package_name,
                       repos = "http://cran.mtu.edu/")
    }
    library(
      package_name,
      character.only = TRUE,
      quietly = TRUE,
      verbose = FALSE
    )
  }
  rm(list = c("package_name", "package_names"))
  
  # Load one package via drat, if needed
  if (!is.element("networkdata", installed.packages()[, 1])) {
    addRepo("schochastics")
    install.packages("networkdata")
  }
  library(
    "networkdata",
    character.only = TRUE,
    quietly = TRUE,
    verbose = FALSE
  )
}

# Because I like these options:
options(show.signif.stars = FALSE)
options(digits = 4)
```


```{r}
# reading in the data
paste0("https://raw.githubusercontent.com/mathbeveridge/gameofthrones/master/data/got-s",1:8,"-edges.csv") -> edges
purrr::map(edges,read_csv) -> edges_tbl
```
I've never watched Game of Thrones, so I want to get an idea of prominent characters based on degree centrality through each season.


## Season 1
```{r}
# season 1
s1 <- graph_from_data_frame(edges_tbl[1])

# proportional to degree centrality
plot(s1, main = "Season 1: Proportional to Degree",
     vertex.size = igraph::degree(s1)/10,
     edge.arrow.size = 0.1,
     vertex.label.cex = 0.67)
```
Tyrion, Ned, Robb, and Robert seem to have high degree centrality, as they have a lot of links to other characters.
I'll keep an eye on these names going forward as I will assume that they are vital characters throughout the show.

## Season 2
```{r}
# season 2
s2 <- graph_from_data_frame(edges_tbl[2])

# proportional to degree centrality
plot(s2, main = "Season 2: Proportional to Degree",
     vertex.size = igraph::degree(s2)/5,
     edge.arrow.size = 0.1,
     vertex.label.cex = 0.67)
```
I see Tyrion and Robb again, in addition to some new names:
Joffrey, Tywin, Arya, and Cersei. Ned and Robert are still around, but don't seem to have as big of an influence as before. Possible that they died? Maybe they fell off and simply aren't as prevalent anymore.

## Season 3
```{r}
# season 3
s3 <- graph_from_data_frame(edges_tbl[3])

# proportional to degree centrality
plot(s3, main = "Season 3: Proportional to Degree",
     vertex.size = igraph::degree(s3)/5,
     edge.arrow.size = 0.1,
     vertex.label.cex = 0.67)
```
Tyrion and Tywin are remaining involved, but I noticed Robb, Catelyn, and Jon start to emerge into the third season. Catelyn and Robb are particularly close to each other (potential relationship?). Let's look out for those three in season 4.

## Season 4
```{r}
# season 4
s4 <- graph_from_data_frame(edges_tbl[4])

# proportional to degree centrality
plot(s4, main = "Season 4: Proportional to Degree",
     vertex.size = igraph::degree(s4)/5,
     edge.arrow.size = 0.1,
     vertex.label.cex = 0.67)
```
Jon is still around, and Sam joins in with a seemingly integral role.
Sansa, Joffrey, Cersei, Jamie, Tywin, Tyrion, and Daenerys seem to have important involvement.
Robb practically disappears, as well as Catelyn, which leads me to believe they either both died, or had diminished involvement in this season for whatever reason.

## Season 5
```{r}
# season 5
s5 <- graph_from_data_frame(edges_tbl[5])

# proportional to degree centrality
plot(s5, main = "Season 5: Proportional to Degree",
     vertex.size = igraph::degree(s5)/5,
     edge.arrow.size = 0.1,
     vertex.label.cex = 0.67)
```
Littlefinger and Stannis are names I haven't seen stick out in the previous plots, so I'll assume they were either introduced this season, or were granted heavier involvement this season. Tyrion, Sansa, and Cersei still stand out as they have been.

## Season 6
```{r}
# season 6
s6 <- graph_from_data_frame(edges_tbl[6])

# proportional to degree centrality
plot(s6, main = "Season 6: Proportional to Degree",
     vertex.size = igraph::degree(s6)/5,
     edge.arrow.size = 0.1,
     vertex.label.cex = 0.67)
```
Can't find Littlefinger on here anymore; did he die? However, I still do see Tyrion, Cersei, and Sansa. In particular, Sansa seems to have an even larger role in this season compared to past seasons.


## Season 7
```{r}
# season 7
s7 <- graph_from_data_frame(edges_tbl[7])

# proportional to degree centrality
plot(s7, main = "Season 7: Proportional to Degree",
     vertex.size = igraph::degree(s7)/5,
     edge.arrow.size = 0.1,
     vertex.label.cex = 0.67)
```
Littlefinger pops back up again, so maybe I was quick to assume he died. Perhaps he did die, but maybe he had some sort of hidden plot or background that caused him to be brought back into the discussion. Jon plays a bigger role in season 7, even outweighing Tyrion and Cersei (who seemed to be prominent in each season).
Davos and Theon are newer names that I hadn't noticed in the previous plots.

## Season 8
```{r}
# season 8
s8 <- graph_from_data_frame(edges_tbl[8])

# proportional to degree centrality
plot(s8, main = "Season 8: Proportional to Degree",
     vertex.size = igraph::degree(s8)/5,
     edge.arrow.size = 0.1,
     vertex.label.cex = 0.67)
```
Lots of people are heavily involved, some of which are familiar faces from the previous plots (e.g. Tyrion, Jaime, Daenerys).

So, I heard that at the end of GOT a lot of the remaining characters die. I presume that there are a lot more people with higher degree centralities in this plot because of some sort of way to tie together all of the remaining prominent characters in a season finale. As a result, you would expect an increase in nodal size for many of the characters as their involvement likely increases, which in turn drives up their degree centrality.
