---
title: "Investigation 5"
author: "John Viviani"
date: "6/28/2020"
output: 
  md_document:
    variant: gfm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

{
  c("conflicted",    # To deal with conflicting function names.
                     # I've had some strangeness with this
                     #  script. I suspect package:conflicted,
                     #  but I don't yet know for sure.
    "data.table",    # Fast data input/output
    "dplyr",         # This is all of tidyverse that gets used here
    "drat",          # Needed for a possible install below 
    "dtplyr",        # dplyr syntax with a data.table backend
    "igraph",        # Basic network tools; we'll use statnet mostly
    "igraphdata",    # Some useful datasets
    "intergraph",    # Translate between igraph and statnet formats
    "statnet",        # A suite of network tools, including ERGM and more
    "tidyverse",
    "vegan"
  ) -> package_names
  
  for (package_name in package_names) {
    if (!is.element(package_name, installed.packages()[, 1])) {
      install.packages(package_name,
                       repos = "http://cran.mtu.edu/")
    }
    library(
      package_name,
      character.only = TRUE,
      quietly = TRUE,
      verbose = FALSE
    )
  }
  rm(list = c("package_name", "package_names"))
  
  # Load one package via drat, if needed
  if (!is.element("networkdata", installed.packages()[, 1])) {
    addRepo("schochastics")
    install.packages("networkdata")
  }
  library(
    "networkdata",
    character.only = TRUE,
    quietly = TRUE,
    verbose = FALSE
  )
}

# Because I like these options:
options(show.signif.stars = FALSE)
options(digits = 4)
```


```{r}
# reading in the data
amazon_E <- fread("~/COLLEGE/GRAD SCHOOL/GDAT622/amazon-2003-03-02.txt")

# cleaning up the edgelist
colnames(amazon_E)[1] <- "FromNodeId"
colnames(amazon_E)[2] <- "ToNodeId"
# replacing zeroes with x to avoid error when making the graph
amazon_E[amazon_E == 0] <- "x"

# converting to a matrix
mat <- as.matrix(amazon_E)

# creating the graph object
g <- graph_from_edgelist(mat, directed = FALSE)

# will take VERY long
# plot(g,
#      edge.arrow.size = 0.05,
#      vertex.size = 0.5)

# let's trying reducing the size of the network
# pruning via louvain method
clus <- cluster_louvain(g)
# it assigned 210 groups
clus

# this alone will take VERY long
# let's try this again later, but after pruning
# plot(g, vertex.color = rainbow(210, alpha = 0.6)[clus$membership],
#      vertex.label = NA,
#      edge.arrow.size = 0.05,
#      vertex.size = 1)
```
Might be worthwhile looking at individual groups before trying to run the entire network.


# Group 210
```{r}
# let's try looking at one of the groups
group210 <- copy(clus[210])

# subsetting from amazon_E based on nodes in group 210
group210_E <- subset(amazon_E, FromNodeId %in% group210$`210`)

g210 <- graph_from_data_frame(group210_E)
 
plot(g210,
     edge.arrow.size = 0.15,
     main = "Group 210")

igraph::betweenness(g210)
igraph::degree(g210)
```
I looked at a particular cluster in this network, which featured the 6 items below. Node 261847 (Music: A Golden Hour of Comedy) was in the center of the cluster.

Id: 261847
title: A Golden Hour of Comedy
  group: Music
  salesrank: 263401
  similar: 0
  categories: 5
   |Music[5174]|Styles[301668]|Miscellaneous[35]|Poetry, Spoken Word & Interviews[603190]|General[63951]
   |Music[5174]|Styles[301668]|Miscellaneous[35]|General[170942]
   |Music[5174]|Styles[301668]|Miscellaneous[35]|Compilations[466080]|Comedy[466088]
   |Music[5174]|Styles[301668]|Miscellaneous[35]|Comedy[63936]|General[466982]
   |Music[5174]|Specialty Stores[468040]|Indie Music[266023]|Miscellaneous[171247]|Comedy & Spoken Word[520240]
  reviews: total: 0  downloaded: 0  avg rating: 0

Id: 10434
title: Rainbow Palace
  group: Music
  salesrank: 27222
  similar: 5  B0000BV0HG  B0000BV0HN  B00000AF5X  B0000BV0HJ  B0000BV0HI
  categories: 1
   |Music[5174]|Styles[301668]|Children's Music[173425]|General[173426]
  reviews: total: 2  downloaded: 2  avg rating: 5
  
Id: 261948
title: What Shall I Draw (What Shall I Do Today Series)
  group: Book
  salesrank: 495249
  similar: 5  074603704X  0746029438  0746028598  0746028024  0439140072
  categories: 1
   |Books[283155]|Subjects[1000]|Children's Books[4]|Arts & Music[2870]|Art[2872]|Drawing[2874]
  reviews: total: 3  downloaded: 3  avg rating: 4.5

Id: 261735
title: Great Days: The John Prine Anthology
  group: Music
  salesrank: 1723
  similar: 5  B0007VROHE  B00000K3LI  B000002I97  B0000005XY  B0000005Y2
  categories: 5
   |Music[5174]|Styles[301668]|Country[16]|General[63695]
   |Music[5174]|Styles[301668]|Folk[32]|Contemporary Folk[598642]|General[63714]
   |Music[5174]|Styles[301668]|Folk[32]|General[63716]
   |Music[5174]|Labels[892976]|Amazon.com Label Stores[301122]|Rhino Records[574566]
   |Music[5174]|Styles[301668]|Folk[32]|Contemporary Folk[598642]|Singer-Songwriters[598644]
  reviews: total: 31  downloaded: 31  avg rating: 5
  
Id: 261736
ASIN: 0520234901
  title: Westward Dharma: Buddhism beyond Asia
  group: Book
  salesrank: 613087
  similar: 5  0520216970  0520213017  0700712046  0195152417  0231108699
  categories: 2
   |Books[283155]|Subjects[1000]|Religion & Spirituality[22]|Buddhism[12279]|General[12282]
   |Books[283155]|Subjects[1000]|Religion & Spirituality[22]|Buddhism[12279]|Dharma[297499]
  reviews: total: 0  downloaded: 0  avg rating: 0

Id: 236491
title: Sat II: Writing 2000-2001 (Sat II. Writing)
  group: Book
  salesrank: 842047
  similar: 5  0764123467  0743241231  0375763015  0743251962  0131828010
  categories: 2
   |Books[283155]|Subjects[1000]|Reference[21]|Education[11628]|Test Guides - College & University[11668]|SAT & PSAT[11682]
   |Books[283155]|Subjects[1000]|Reference[21]|Test Prep Central[11904]|General[408252]
  reviews: total: 8  downloaded: 8  avg rating: 3.5

Three songs and three books were featured in this cluster. 
The three songs were pretty different from one another, with A Golden Hour of Comedy being categorized as a comedic/indie song, Rainbow Palace being a children's song, and Great Days: The John Prine Anthology being a country/folk song.
The three books were also relatively unrelated to one another.
What Shall I Draw (What Shall I Do Today Series) is a children's art book, Westward Dharma: Buddhism beyond Asia revolves around religion (Buddhism) and spirituality, and Sat II: Writing 2000-2001 (Sat II. Writing) is an educational book regarding SAT preparation.

Regarding the books, there at least seems to be an educational theme to them, although it applies to people of varying age groups (e.g. What Shall I Draw (What Shall I Do Today Series) being a book to teach children art, Sat II: Writing 2000-2001 (Sat II. Writing) being something that a highschool student would use, and Westward Dharma: Buddhism beyond Asia being something that a college student may need for a liberal arts course).


# Community Detection Algorithm
```{r}
amazon_spinglass <- igraph::cluster_spinglass(g)
plot(amazon_spinglass, g)
```
Seeing as this is a large amount of data, it will be difficult to get anything meaningful from the plot. We'll need to get this network to be smaller and smaller.


# Pruning by Degree
```{r}
g_degree <- igraph::degree(g)
max(g_degree)
min(g_degree)
mean(g_degree)

# getting rid of any nodes with a degree less than 100
g_sub <- delete_vertices(g, V(g)[igraph::degree(g) < 100])

plot(g_sub)

# here's the code from the louvain cluster shown earlier
# now applied to g_sub
plot(g_sub, vertex.color = rainbow(210, alpha = 0.6)[clus$membership],
     vertex.label = NA,
     edge.arrow.size = 0.15,
     vertex.size = 8.5)
```


# Pruning by Degree Centrality then Betweenness Centrality
```{r}
g_sub2 <- induced.subgraph(g, vids = V(g)[igraph::degree(g)] > 50)

plot(g_sub2)
# we've filtered for degree values above 50; however, it's still difficult to view

# let's prune this subgraph by betweenness
g_sub2_bw <- igraph::betweenness(g_sub2)
max(g_sub2_bw)
min(g_sub2_bw)
mean(g_sub2_bw)

g_sub3 <- induced.subgraph(g_sub2, vids = V(g_sub2)[igraph::betweenness(g_sub2) > 250])

plot(g_sub3,
     vertex.size = 8.5,
     vertex.label.cex = 0.80,
     main = "Degree > 50 & Betweenness > 250")
# much easier to visualize
```
I figured filtering for relatively high values of degree would be sound as we'd able to see those nodes that have high links between other nodes. Following this, filtering for a relatively high betweenness allows us to understand which nodes are integral parts of the network, as many nodes will need to pass through those that have a higher betweenness centrality.

In this plot, we see that nodes 7628, 3464, and 21 are gatekeepers, as each node must go through them in order to reach the nodes on the opposite side. Listed below are what those items were according to the Amazon metadata:

Id: 3464
title: Ultimate Sniper
  group: Video
  salesrank: 24375
  similar: 5  B00004XQPE  1571199454  6305120862  B00007GCYU  B000056HJ4
  categories: 2
   |[139452]|VHS[404272]|Genres[404274]|Documentary[508530]|Military & War[169897]|General[169899]
   |[139452]|VHS[404272]|Genres[404274]|Special Interests[135]|General[407858]
  reviews: total: 5  downloaded: 5  avg rating: 4

Id: 7628
title: Stories for a Teacher's Heart (Stories For the Heart)
  group: Book
  salesrank: 873929
  similar: 0
  categories: 3
   |Books[283155]|Subjects[1000]|Literature & Fiction[17]|Books & Reading[9988]|Reference[10011]
   |Books[283155]|Subjects[1000]|Literature & Fiction[17]|General[10125]|Classics[10127]
   |Books[283155]|Subjects[1000]|Religion & Spirituality[22]|Spirituality[12809]|Inspirational[12817]
  reviews: total: 0  downloaded: 0  avg rating: 0
  
Id: 21
title: The Time Machine
  group: DVD
  salesrank: 795
  similar: 5  B00007JMD8  6305350221  B00004RF9B  B00005JKFR  B00005NG6A
  categories: 26
   |[139452]|DVD[130]|Genres[404276]|Drama[163379]|General[163390]
   |[139452]|DVD[130]|Genres[404276]|Science Fiction & Fantasy[163431]|Fantasy[163440]
   |[139452]|DVD[130]|Genres[404276]|Science Fiction & Fantasy[163431]|General[163442]
   |[139452]|DVD[130]|Genres[404276]|Science Fiction & Fantasy[163431]|Classic Sci-Fi[292650]
   |[139452]|DVD[130]|Genres[404276]|Science Fiction & Fantasy[163431]|Monsters & Mutants[292662]
   |[139452]|DVD[130]|Genres[404276]|Science Fiction & Fantasy[163431]|By Theme[292669]|Time Travel[292667]
   |[139452]|DVD[130]|Actors & Actresses[404278]|( B )[411316]|Bissell, Whit[413160]
   |[139452]|DVD[130]|Actors & Actresses[404278]|( C )[416120]|Cabot, Sebastian[416132]
   |[139452]|DVD[130]|Actors & Actresses[404278]|( F )[422476]|Frees, Paul[423942]
   |[139452]|DVD[130]|Actors & Actresses[404278]|( H )[426368]|Helmore, Tom[427584]
   |[139452]|DVD[130]|Actors & Actresses[404278]|( L )[432148]|Lloyd, Doris[433832]
   |[139452]|DVD[130]|Actors & Actresses[404278]|( M )[434574]|Mimieux, Yvette[437458]
   |[139452]|DVD[130]|Actors & Actresses[404278]|( T )[448792]|Taylor, Rod[449112]
   |[139452]|DVD[130]|Actors & Actresses[404278]|( Y )[453438]|Young, Alan[453620]
   |[139452]|DVD[130]|Directors[403502]|( P )[460606]|Pal, George[460622]
   |[139452]|DVD[130]|Genres[404276]|Art House & International[163313]|By Theme[502916]|Costume Adventures[502980]
   |[139452]|DVD[130]|Genres[404276]|Drama[163379]|Classics[524228]
   |[139452]|DVD[130]|Special Features[408328]|Today's Deals in DVD[409298]|Deals Under $15[565160]
   |[139452]|DVD[130]|Special Features[408328]|Titles[579510]|( T )[579550]
   |[139452]|DVD[130]|Genres[404276]|Art House & International[163313]|By Country[284926]|United Kingdom[579580]|General[579588]
   |[139452]|DVD[130]|Specialty Stores[498862]|Studio Specials[468374]|Warner Home Video[515794]|Drama[600318]
   |[139452]|DVD[130]|Specialty Stores[498862]|Studio Specials[468374]|Warner Home Video[515794]|All Titles[600330]
   |[139452]|DVD[130]|Specialty Stores[498862]|Studio Specials[468374]|Warner Home Video[515794]|Classics[600334]
   |[265523]|Amazon.com Stores[285080]|Amazon.com Outlet[517808]|Categories[526028]|DVD Outlet[734006]|Deals Under $15[734042]
   |[139452]|DVD[130]|Genres[404276]|Science Fiction & Fantasy[163431]|Futuristic[735728]
   |[139452]|DVD[130]|Specialty Stores[498862]|Studio Specials[468374]|Warner Home Video[515794]|DVDs Under $15[1038542]
  reviews: total: 140  downloaded: 140  avg rating: 4.5

The Time Machine is a popular item with a sales rank of 795.


# Scaling g_sub3 by Eigenvector Centrality
```{r}
# scaling g_sub3 by eigenvector centrality
plot(g_sub3,
     vertex.size = igraph::eigen_centrality(g_sub3)$vector*5,
     edge.arrow.size = 0.125,
     main = "g_sub3 Scaled by Eigenvector Centrality")
```
Nodes 4429, 5120, 2353 all stood out when this network was scaled by Eigenvector centrality. This indicates that these node Their items are listed below:

Id: 4429
title: Harley-Davidson Panheads, 1948-1965/M418
  group: Book
  salesrank: 147799
  similar: 5  0760310629  0967274400  0879389346  0892875666  076030226X
  categories: 4
   |Books[283155]|Subjects[1000]|Home & Garden[48]|Antiques & Collectibles[5066]|Transportation[5076]
   |Books[283155]|Subjects[1000]|Nonfiction[53]|Automotive[10503]|Motorcycles[10520]|General[10521]
   |Books[283155]|Subjects[1000]|Nonfiction[53]|Automotive[10503]|Motorcycles[10520]|Repair & Performance[10525]
   |Books[283155]|Subjects[1000]|Nonfiction[53]|Transportation[11934]|General[11947]
  reviews: total: 3  downloaded: 3  avg rating: 4.5
    1999-1-27  cutomer: A1X0D5EB937DEI  rating: 5  votes:  19  helpful:  19
    2001-4-14  cutomer:  A7UGKKVF6PH21  rating: 5  votes:   8  helpful:   7
    2003-11-15  cutomer: A1Y3J71SBICPX9  rating: 4  votes:   0  helpful:   0
    
Id: 5120
title: Tae Kwon Do for Women
  group: Book
  salesrank: 844576
  similar: 2  0816038392  0873644921
  categories: 4
   |Books[283155]|Subjects[1000]|Health, Mind & Body[10]|Mental Health[4682]|Abuse & Self Defense[4683]|Self Defense[4686]
   |Books[283155]|Subjects[1000]|Sports[26]|Individual Sports[16533]|Martial Arts[16571]|General[16575]
   |Books[283155]|Subjects[1000]|Sports[26]|Individual Sports[16533]|Martial Arts[16571]|Tai Kwon Do[16581]
   |Books[283155]|Subjects[1000]|Sports[26]|General[11086921]
  reviews: total: 0  downloaded: 0  avg rating: 0

Id: 2353
title: Committed
  group: Music
  salesrank: 437762
  similar: 0
  categories: 4
   |Music[5174]|Styles[301668]|International[33]|General[63848]
   |Music[5174]|Styles[301668]|Pop[37]|General[67172]
   |Music[5174]|Specialty Stores[468040]|Indie Music[266023]|International[171245]|General[520182]
   |Music[5174]|Specialty Stores[468040]|Indie Music[266023]|Pop[171249]|General[520274]
  reviews: total: 4  downloaded: 4  avg rating: 5
    2002-1-30  cutomer:  APONWVS6M0OHF  rating: 5  votes:   1  helpful:   1
    2002-2-1  cutomer: A2Q4GP8S4F6UXO  rating: 5  votes:   3  helpful:   3
    2002-2-3  cutomer: A3GJYD4IML3UEK  rating: 5  votes:   2  helpful:   2
    2005-5-14  cutomer:  AEGNAFJJ2W1CW  rating: 5  votes:   0  helpful:   0

Two books on completely unrelated topics (Harley-Davidson motorcycles and women's Tae Kwon Do) and an indie pop song (Committed). It's difficult to say as to why these are particularly important, so I would assume that they happen to be surrounded by other nodes that play an integral role in this pruned network.


